---
title: "Expert advice from experts"
author:
- familyname: Curie
  othernames: Marie
  address: University of Paris
  qualifications: Nobel Prize, PhD
- familyname: Curie
  othernames: Pierre
  address: University of Paris
  qualifications: Nobel Prize, PhD
email: mcurie.notreal@gmail.com
phone: (03) 9905 2478
department: Department of\newline Econometrics &\newline Business Statistics
organization: Acme Corporation
bibliography: references.bib
biblio-style: authoryear-comp
linestretch: 1.5
output:
  monash::report:
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    includes:
      in_header: preamble.tex
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
    toc: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache=TRUE, messages=FALSE, warning=FALSE)
library(ggplot2)
library(readr)
library(tidyverse)
library(dplyr)

```

```{r}

covid <- read_csv(here::here("data/worldwidecases.csv"))

```




```{r covid-europe, echo = FALSE, fig.align = "center", fig.width = 6, fig.cap = "Rates of covid cases over time for selected countries"}

covidrate_vis <- covid %>%
  mutate(date= as.Date(dateRep, format = "%d/%m/%y"),
         cases_rates = ((1000*cases/popData2018) + 0.01),
         dead_rates = ((1000*deaths/popData2018) +0.01)) %>%
  dplyr::filter(date != "2020-12-31") 
  
covidrate_vis %>%
  #group_by(countriesAndTerritories, date) %>%
  #summarize_at(vars(cases, deaths), cumsum) %>%
  dplyr::filter(countriesAndTerritories %in%
                  c("Italy", "Germany", "Greece", "Switzerland", "Sweden", "France")) %>%
  ggplot(aes(x = date, y = cases_rates)) +
  geom_line(color = "#1F9E8E") +
  facet_wrap(~countriesAndTerritories) +
  theme_bw() +
  ggtitle("Covid cases (rates)")

covidrate_vis


```


### Section 1

Based on Figure \ref{fig:covid-europe}, it can be seen that Switzerland had the highest COVID cases rate among the six countries observed. In contrast, Greece's COVID cases rate was the lowest and also the most relatively stable compared to the other countries. The reference is as follows. @Gibsone252899


In figure \ref{fig:covidgraph}, we observe the corona virus rates of a number european countries . Here is a reference to an article @BC64 
